Assessing Power of the California Microhap Baseline for GSI (and calculating Fst)

### 2024-05-07 002-GSI_and_Fst.Rmd
Start supplement.  Write more
Committing 002 before doing a lot of pruning of it
I want to use the new baseline with the hapstrs and I also want to just do it all with the LFAR included (I don't really care about the Fst's being inflated from the LFAR---we kind of want that, ultimately, I think.)

@@

investigate the ones that are in the wrong repunit, and look at their
scaled_repu_likelihoods, the others.
```{r}
ta_corr_lfar <- top_ass_w_lfar %>%
  filter(repunit == inferred_repunit)
ta_wrong_lfar <- top_ass_w_lfar %>%
  filter(repunit != inferred_repunit) %>%
  arrange(collection, repu_sclike) %>%
  group_by(collection) %>%
  mutate(y = 190 + (70/9) * 1:n())

@@

ggsave(gbp, filename = "tex/images/num-alle-barplot.pdf", width = 4, height = 3)
```

>>>>

repu_likes <- full_plus_lfar_sa %>%
  group_by(indiv, collection, repunit, inferred_repunit) %>%
  summarise(repu_sclike = sum(scaled_likelihood)) %>%
  ungroup()

@@

## Identifying fish erroneously included in some collections

The occurrence of winter-run-assigned fish amongst the spring run collections is
a clear indicator that there are some fish in the collections that do not belong
with one another.  The same occurs amongst the fall and the spring run, I expect.

Our goal here is to examine the likelihoods with which fish are assigned to
different reporting units and come up with a common-sense and defensible approach
for discarding individuals that don't belong in the collections they were sampled
from.

We start by tallying up the misassigned fish---those that have a repunit and an
inferred repunit that differ:
```{r}
misassigned_ones <- top_ass_w_lfar %>%
  filter(repunit != inferred_repunit) %>%
  count(repunit, inferred_repunit)

misassigned_ones
```

For each of these 6 pairs, I want to make a scatterplot that shows the repunit
likelihoods of all the fish _from either the repunit or the inferred_repunit_.
The x-axis will be the likelihood for the repunit and the y-axis will be the
likelihood for the inferred_repunit.  So, there is some weird prep to get
this all together.  
```{r}
MO2 <- misassigned_ones %>%
  rename(
    Foc_repunit = repunit,
    Foc_inferred_repunit = inferred_repunit
  )

tmp <- lapply(1:nrow(MO2), function(i) {
  repu_likes %>%
    filter(
      (repunit == MO2$Foc_repunit[i] | repunit == MO2$Foc_inferred_repunit[i]) &
        (inferred_repunit == MO2$Foc_repunit[i] | inferred_repunit == MO2$Foc_inferred_repunit[i])
    ) %>%
    mutate(
     Foc_repunit =  MO2$Foc_repunit[i],
     Foc_inferred_repunit = MO2$Foc_inferred_repunit[i],
     .before = repunit
    )
}) %>%
  bind_rows() %>%
  arrange(indiv, Foc_repunit, Foc_inferred_repunit)

for_plots <- tmp %>%
  mutate(
    rep = ifelse(Foc_repunit == repunit, "rep", "inf"),
    inf = ifelse(Foc_inferred_repunit == inferred_repunit, "inf", "rep")
  ) %>%
  #count(Foc_repunit, Foc_inferred_repunit, repunit, inferred_repunit, rep, inf)
  select(-repunit, -inferred_repunit) %>%
  pivot_wider(names_from = c(rep, inf), names_sep = "_to_", values_from = repu_sclike) %>%
  mutate(condition = str_c(Foc_repunit, " misassigned to ", Foc_inferred_repunit), .after = Foc_inferred_repunit)
```

Now we should be able to facet wrap those:
```{r}
ggplot(for_plots) +
  geom_point(aes(x = inf_to_rep, y = inf_to_inf, colour = Foc_inferred_repunit)) +
  geom_point(aes(x = rep_to_rep, y = rep_to_inf, colour = Foc_repunit)) +
  facet_wrap(~condition) +
  scale_colour_manual(values = repunit_colors)

So, for each of the six plots, I will need four different repu_sclike's:
For example, for the `repunit = CV-Fall` and `inferred_repunit = CV-Spring` case
we will need to have the repu_sclikes for CV-Fall fish being calculated for CV-Fall
and CV-Spring, and for the CV-Spring fish being calculated for CV-Spring and CV-Fall.

Now, we want to use this to semi-join to get all the likelihoods for these scenarios,
whether or not they were misassigned. 
```{r}
focal_comparisons <- repu_likes %>%
  semi_join(misassigned_ones, by = join_by(repunit, inferred_repunit))
```

And we are going to want to compare these to all the likelihoods of being
from the actual repunit that the fish was col

Now, I want to look at these different comparisons _pairwise_, so we will
just pivot it wider and then look at different columns in there.  This isn't
super "tidy" but I think it should work OK:
```{r}
focal_comparisons %>%
  pivot_wider(names_from = inferred_repunit, values_from = repu_sclike)
```

And I want to look at the observed distribution of these scores in for each
comparison, colored by repunit.
```{r}
ggplot(focal_comparisons, aes(x = )
```

First thing I am going to do is plot histograms of the,
max likelihoods for all of the ones from each repunit.
```{r}
repunit_order <- unique(pop_labels$repunit)
repu_likes %>%
  mutate(
    repunit_f = factor(repunit, levels = repunit_order),
    inferred_repunit_f = factor(inferred_repunit, levels = repunit_order),
  ) %>%
  ggplot() +
  geom_histogram(aes(x = repu_sclike, fill = repunit_f), colour = "black", linewidth = 0.16) + 
  facet_grid(repunit_f ~ inferred_repunit_f) + 
  scale_fill_manual(values = repunit_colors) +
  theme_bw()
```

```{r}
ta_corr_lfar <- top_ass_w_lfar %>%
  filter(repunit == inferred_repunit)
ta_wrong_lfar <- top_ass_w_lfar %>%
  filter(repunit != inferred_repunit) %>%
  arrange(collection, repu_sclike) %>%
  group_by(collection) %>%
  mutate(y = 190 + (70/9) * 1:n())

@@

ggsave(gbp, filename = "tex/images/num-alle-barplot.pdf", width = 4, height = 3)

numa
```
